Designing Types for R, Empirically

### 2020-05-16 paper/main.tex
Fix types

type `data.tree::Traverse` <class<`Node`, `R6`>, character[], any, any> => list<any>;

type `openssl::decrypt\_envelope` <raw[], raw[], raw[], class<`key`, `rsa`>, any> => raw[];

dbplyr:type `set\_win\_current\_group` <null | character[]> => (character[] | null);

type `sha256` <raw[], null | raw[]> => raw[];

type `initparam` <? double, any, any, any, character, character, logical, double[], double[], any> => double[];

>>>>

$$type `data.tree::Traverse` \FUN{\CLASS{`Node`, `R6`}, ~\VEC\chr, \any, \any}\LIST\any;$$

$$type `openssl::decrypt\_envelope` \FUN{~\VEC\raw, ~\VEC\raw, ~\VEC\raw, \CLASS{`key`, `rsa`}, \any}~\VEC\raw;$$

$$dbplyr:type `set\_win\_current\_group` \FUN{? ~\VEC\chr}? ~\VEC\chr;$$

$$type `sha256` \FUN{~\VEC\raw, ? ~\VEC\raw}~\VEC\raw;$$

$$type `initparam` \FUN{? \dbl, \any, \any, \any, \chr, \chr, \lgl, ~\VEC\dbl, ~\VEC\dbl, \any}~\VEC\dbl;$$
